---
title: "Policy Support: Individual Predictors"
output:
  html_document:
    toc: true
    toc_depth: 3
    keep_md: no
    toc_float: true
    code_folding: hide
---
The support for harm reduction policies is evaluated in association with individual features of the sample. 

<!-- These two chunks should be added in the beginning of every .Rmd that you want to source an .R script -->
<!--  The 1st mandatory chunck  -->
<!--  Set the working directory to the repository's base directory -->
```{r, echo=F, message=F} 
#Don't combine this call with any other chunk 
# cat("Working directory: ", getwd()) # check where you are
  library(knitr)
# Rmd is in "./reports/reportA/reportA.Rmd", but now the root is "./"
  knitr::opts_knit$set(root.dir='../../') 
```

<!--  The 2nd mandatory chunck  -->
<!-- Set the report-wide options, and point to the external code file. -->
```{r set_options, echo=F}
# set options shared by all chunks
opts_chunk$set(
  results='show', 
  message = TRUE,
  comment = NA, 
  tidy = FALSE,
  fig.height = 5, 
  fig.width = 9, 
  out.width = "900px",
  fig.path = 'figure_rmd/',     
  dev = "png",
  dpi = 200
  # fig.path = 'figure_pdf/',     
  # dev = "pdf"#,
  # dev.args=list(pdf = list(colormodel = 'cmyk'))
)
echoChunks <- TRUE
options(width=120) #So the output is 50% wider than the default.
# connect to the file with the underlying R script  
read_chunk("./analysis/2-policy-support/policy-support-model-1.R") 
```

## Environment 
This section offers technical detail on the environment and data preparation. Non-technical readers should feel free to skip. 
```{r load-packages, echo=echoChunks, message=FALSE}
```

```{r load-sources, echo=echoChunks, message=FALSE}
```

```{r declare-globals, echo=echoChunks, results='show', message=FALSE}
```

```{r load-data, echo=echoChunks, results='hide', message=FALSE}
```

```{r inspect-data, echo=echoChunks, results='show', message=FALSE}
```

```{r add-new-names, echo=echoChunks, results='show', message=FALSE}
```

```{r tweak-data, echo=echoChunks, results='show', message=FALSE}
```

```{r groom-predictors, echo=echoChunks, results='hide', message=FALSE}
```


# Target: Policy Support (Q15)

```{r target-outcome, echo=FALSE, results='show', message=FALSE, out.width ="900px", warning=FALSE, cache = T}
```

# Explanatory Variables

While ```r dsm1 %>% nrow()``` observation of the total score on Harm Reduction Policies support were available, some of the predictors were missing or had underrepresented levels. We remove these observation forr the ease of interpretation and modeling parsimony. 

```{r}
dsm1 %>% group_by(sex) %>% count()
sex_valid_set <- c("Male","Female")
cat(dsm1 %>% filter(!sex %in%  sex_valid_set) %>% nrow(), " observations were dropped that did not belong to the set (", paste0(sex_valid_set, collapse = " , "), ")")


dsm1 %>% group_by(class_standing) %>% count()
class_standing_valid_set <- c("Freshman", "Sophomore","Junior","Senior")
cat(dsm1 %>% filter(!class_standing %in%  class_standing_valid_set) %>% nrow(), " observations were dropped that did not belong to the set (", paste0(class_standing_valid_set, collapse = " , "), ")")


dsm1 %>% group_by(religion) %>% count()
religion_valid_set <- c("Very important", "Moderately important", "Not important")
cat(dsm1 %>% filter(!religion %in%  religion_valid_set) %>% nrow(), " observations were dropped that did not belong to the set (", paste0(religion_valid_set, collapse = " , "), ")")

cat(dsm1 %>% filter(is.na(knowledge_oud_tx)) %>% nrow(), " cases were dropped because they missed the value on `knoweldge_oud_tx` variable")

```

Thus, the total of ```r (nrow(dsm1) - nrow(dsm2))``` of observation was removed, resulting in ```r nrow(dsm2)``` complete cases, the descriptive statistics for which are presented below. 

```{r explanatory-variables, echo=TRUE, results='show', message=FALSE, out.width ="900px", warning=FALSE, cache = T}
```


<!-- ```{r support-1, echo=FALSE, results='show', message=FALSE, out.width ="900px", warning=FALSE, cache = T} -->
<!-- ``` -->

<!-- ```{r support-2, echo=FALSE, results='show', message=FALSE, out.width ="900px", warning=FALSE, cache = T} -->
<!-- ``` -->

<!-- ```{r support-3, echo=FALSE, results='show', message=FALSE, out.width ="900px", warning=FALSE, cache = T} -->
<!-- ``` -->

<!-- # (Q4) Knowledge of OUD Tx -->

<!-- ```{r q4, echo=FALSE, results='show', message=FALSE, out.width ="900px", warning=FALSE, cache = T} -->
<!-- ``` -->


<!-- ```{r knowledge-1, echo=FALSE, results='show', message=FALSE, out.width ="900px", warning=FALSE, cache = T} -->
<!-- ``` -->

<!-- ```{r knowledge-2, echo=FALSE, results='show', message=FALSE, out.width ="900px", warning=FALSE, cache = T} -->
<!-- ``` -->

<!-- ```{r knowledge-3, echo=FALSE, results='show', message=FALSE, out.width ="900px", warning=FALSE, cache = T} -->
<!-- ``` -->
